% Please do not change the document class
\documentclass[11pt]{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title+
\title{Continuing Personal Developement Report}


% Please do not change the subtitle
\subtitle{COMP230 - CPD Reports}

% Please put your student number in the author field
\author{1605913}



\begin{document}

\maketitle


\section*{Introduction}

I am not sure what my specific career goals are at this time, but I feel like I would like to work in Indie development rather than an AAA company, the reason for this is like the freedom to do what I want rather than being forced to do a project that I may not like. Although at this point I am having very bad motivation issues with the course and am continuing to doubt myself and procrastinate from work which is then making me feel even worse, so I am going to try for the next semester to break this cycle.
I feel like I have learnt quite a lot while on this course in a few different coding languages although I would rather focus on one language for a bit longer rather than chop and change languages every so often. The five key challenges that I have faced over the last semester are communication, motivation, time management, programming ability and seeking out help. 

\section{Communication}
This year I have been incredibly bad at communicating with my team although it has gotten better through the semester, it can always be better, this has hindered my work incredibly and has stopped me achieving the results that I want. This has set back work by at least seven weeks as group game team that I am part of scrapped the game we were making because we were not communicating with each other and saying that we hated it and did not have the motivation to work on it. Even as going as far as making excuses to not turn up to meetings and working on it. Which is why this being one the main problem I intend to address over the next semester.

\section{Motivation}
The main problem that I have encountered over this semester is that I do not have as much motivation for this course as I did last year, and this is hindering me in such a bad way that I feel like there is no point in continuing with the course. The reason for this is because if I cannot find the motivation to work then my grades are going to be low and this also gives me unnecessary stress, but I intend to stay on top of my work as a last-ditch effort to save myself from the lack of motivation. If I can't pull myself out of this hole that I have dug, then I will have to look at how I can fix it or look for alternatives as now I feel like I have let myself down by giving myself such terrible grades.

\section {Time Management}
This is the second main problem that I am having now as I took a part-time job in October as I could not pay my rent, I do not regret taking it as I have gained valuable life skills from it and my confidence has been boosted incredibly which was a problem that not only affected my work but my life in general. Although I am keeping my part-time job I am cutting the number of hours down by a lot as the number of hours I worked was too much to balance work life and university life this is not including trying to have a social life on top of this. Therefore, time management is something that I will address this coming semester by organising myself a lot more than I have in the past.

\section {Programming Ability}
In terms of programming ability, I feel like my ability is very low compared to my peers this links back to being motivated issues as I can't bring myself to engage in extracurricular activities involving programming which means my programming level is very low and this, in turn, makes me give up on problems quite easily as I feel like I am never going to be able to complete it. This has been shown through COMP 220 where I have had to submit the work late because I keep giving up on it because I feel that I do not have the ability to complete it. I am hoping that this next semester by keeping on top of my work I will have adequate time to find problems with my work and find a workaround instead of leaving it to the last minute.

\section {Seeking Out Help}
This year I have been incredibly bad at seeking out help for my work this is also a reason that my work has been of a very low standard, for this reason, I am going to be asking for help on a regular basis this coming semester. As I feel like I could have at least avoided a few of the problems I have discussed before if I had asked for help. or at least get some extracurricular activities to do with the topic being discussed as I feel like that will improve my work ethic and my programming proficiency.

\section*{Conclusion}
In this report, I have identified 5 key skills that I need to work on in the coming semester and how I can improve them hopefully. These will hopefully not become burdens for the rest of the semester as I plan on focusing on these problems to improve my work and motivation towards the course.




\bibliographystyle{ieeetran}
\bibliography{References}

\end{document}